%!TeX root=thesis.tex

\appendix
\chapter{Crowdastro Package}
\label{cha:crowdastro}

As part of this thesis, we developed an open source Python package called
\emph{crowdastro}, containing methods for machine learning on the
cross-identification task, and implementations of many of the methods described
here. In this appendix, we briefly describe how to obtain this package, and list
the submodules available.

\section{Obtaining and Using Crowdastro}

    The source code for crowdastro is available on GitHub at
    \url{http://github.com/chengsoonong/crowdastro}. Crowdastro can also be
    installed through pip, by running \texttt{pip3 install crowdastro}. The code
    is MIT licensed.

    The crowdastro package can be imported into Python or used with the
    command-line interface. Documentation for the command-line interface is
    available on Read~the~Docs at \url{https://crowdastro.readthedocs.io}.

\section{Submodules}
    \label{sec:crowdastro-submodules}

    In this section, we document the main submodules in crowdastro.

    \subsection{active\_learning}
    \label{sec:crowdastro-active-learning}

        \texttt{crowdastro.active\_learning} contains classes that simulate
        active learning tasks with different sampling methods. These all
        implement the same methods, and so can be used as drop-in replacements
        for each other.

        Samplers have access to a pool of unlabelled data and an array of known
        labels. They also have a \texttt{sample\_index} method that returns the
        index of an unlabelled data point to query an expert for the label, and
        a \texttt{sample\_indices} method that returns a list of such indices
        for bulk training. They also have an \texttt{add\_label} method to add
        the retrieved label to the array of known labels, and a
        \texttt{add\_labels} method which takes a list of such labels for bulk
        training.

        \subsubsection{qbc\_sampler}
        \label{sec:crowdastro-qbc-sampler}

            \texttt{crowdastro.active\_learning.qbc\_sampler} contains a class
            \texttt{QBCSampler} that simulates query-by-committee as described
            in Section \ref{sec:qbc}. The committee is composed of a
            user-defined number of logistic regression classifiers trained on a
            user-defined percentage of the labelled data. The
            \texttt{QBCSampler} also keeps a single logistic regression called
            the \emph{reference classifier} which is trained on all known
            labels; it is this classifier that is used to compute the balanced
            accuracy to avoid underreporting of accuracy due to sampling.

        \subsubsection{random\_sampler}
        \label{sec:crowdastro-random-sampler}

            \texttt{crowdastro.active\_learning.random\_sampler} contains
            classes that simulate an active learning task with passive sampling.
            There are two such classes:
            \begin{itemize}
                \item \texttt{RandomSampler}, which samples completely at
                    random,
                \item \texttt{BalancedSampler}, which samples evenly from binary
                    classes.
            \end{itemize}

        \subsubsection{sampler}
        \label{sec:crowdastro-sampler}

            \texttt{crowdastro.active\_learning.random\_sampler} contains the
            \texttt{Sampler} base class for other samplers.

        \subsubsection{uncertainty\_sampler}
        \label{sec:crowdastro-uncertainty-sampler}

            \texttt{crowdastro.active\_learning.uncertainty\_sampler} contains a
            class \texttt{ConfidenceUncertaintySampler} that simulates binary
            uncertainty sampling as described in Section
            \ref{sec:uncertainty-sampling}.

    \subsection{classifier}

        \texttt{crowdastro.classifier} contains a \texttt{RGZClassifier} object
        which attempts to locate the host galaxy of a given ATLAS object using
        the methods developed in this thesis. The nearby galaxy with the highest
        probability of containing an AGN is selected as the associated host
        galaxy. The module also contains a \texttt{RGZCommittee} object which
        could be used to estimate information content of ATLAS objects as
        suggested in Section \ref{sec:al-rgz-ideal-experiment}.

    \subsection{compile\_cnn}

        \texttt{crowdastro.compile\_cnn} uses Keras to compile a convolutional
        neural network model and save the output as JSON.

    \subsection{consensuses}

        \texttt{crowdastro.consensuses} finds the consensus label of each galaxy
        using crowd labels from Radio Galaxy Zoo. This is referred to as the
        Radio Galaxy Zoo majority vote throughout this thesis. A major part of
        this module is the conversion of real-valued labels (i.e. the location
        that the volunteer chose as the location of the host galaxy) into binary
        labels, which is achieved by fitting the Gaussian mixture model with the
        lowest value of the Bayesian information criterion. More details on the
        methods implemented in this module will appear in \citet{atlas-ml}.

    \subsection{crowd}
    \label{sec:crowdastro-crowd}

        \texttt{crowdastro.crowd} contains classes for crowd learning. Both
        classes implement the same methods, and so can be used as drop-in
        replacements for each other. The module also contains some helper
        functions for crowd labels and related experiments.

        \subsubsection{raykar}
            \label{sec:crowdastro-raykar}

            \texttt{crowdastro.crowd.raykar} is an implementation of the crowd
            learning algorithm developed by \citet{raykar10}, described here in
            Section \ref{sec:raykar}. The module provides a
            \texttt{RaykarClassifier} object which implements a modified
            scikit-learn interface.

        \subsubsection{util}
            \label{sec:crowdastro-util}

            \texttt{crowdastro.crowd.util} contains useful functions for dealing
            with crowd labels and performing related experiments shown in this
            thesis. These functions are:
            \begin{itemize}
                \item \texttt{balanced\_accuracy}, which computes the balanced
                    accuracy of a classifier against a test set,
                \item \texttt{crowd\_label}, which simulates the crowd labelling
                    task as described in Section \ref{sec:crowd-simulation},
                \item \texttt{majority\_vote}, which computes the majority vote
                    of a set of crowd labels,
                \item \texttt{logistic\_regression}, a simple implementation of
                    the logistic regression function (Equation
                    \ref{eq:logistic-regression}).
            \end{itemize}

        \subsubsection{yan}
            \label{sec:crowdastro-yan}

            \texttt{crowdastro.crowd.yan} is an implementation of the crowd
            learning algorithm developed by \citet{yan10}, described here in
            Section \ref{sec:yan}. The module provides a \texttt{YanClassifier}
            object which implements a modified scikit-learn interface.

    \subsection{experiment}
    \label{sec:crowdastro-experiment}

        \texttt{crowdastro.experiment} contains all the experiments run for this
        thesis. The scripts in this module can be executed from the command
        line, e.g.

        \begin{center}
            \texttt{python3 -m crowdastro.experiment.experiment\_name}
        \end{center}

    \subsection{generate\_annotator\_labels}

        \texttt{crowdastro.generate\_annotator\_labels} generates binary labels
        for each labeller in Radio Galaxy Zoo by assigning the nearest galaxy to
        labellers' clicks a label of $1$, and assigning all other seen galaxies
        a label of $0$. If a galaxy is never seen by a given labeller, then the
        associated label is masked and not used in future calculations. This is
        referred to as the raw Radio Galaxy Zoo labels in this thesis.

    \subsection{generate\_cnn\_outputs}

        \texttt{crowdastro.generate\_cnn\_outputs} runs a trained convolutional
        neural network on radio patches to obtain features as described in
        Section \ref{sec:radio-features}.

    \subsection{generate\_test\_sets}

        \texttt{crowdastro.generate\_test\_sets} generates training and testing
        sets for use in experiments. This ensures that training and testing
        labels are consistent across experiments, and also that no testing data
        is used to train the convolutional neural network.

    \subsection{generate\_training\_data}

        \texttt{crowdastro.generate\_training\_data} generates vector
        representations of training instances, as well as generating associated
        labels and metadata.

    \subsection{import\_data}

        \texttt{crowdastro.import\_data} imports and standardises data used for
        other modules, including the ATLAS catalogue and images, the WISE
        catalogue, the SWIRE catalogue, the \citeauthor{norris06} catalogue, and
        the \citeauthor{fan15} catalogue.

    \subsection{plot}

        \texttt{crowdastro.plot} contains functions for generating the plots in
        this thesis.

    \subsection{rgz\_data}

        \texttt{crowdastro.rgz\_data} contains low-level functions for handling
        the Radio Galaxy Zoo database.

    \subsection{train\_classifier}

        \texttt{crowdastro.train\_classifier} trains and stores a logistic
        regression classifier on the galaxy classification task.

    \subsection{train\_cnn}

        \texttt{crowdastro.train\_cnn} trains a convolutional neural network on
        the galaxy classification task using a subset of training data. The
        training set is generated in\\\texttt{crowdastro.generate\_test\_sets}
        to ensure that it is held out of testing sets.
